\section{Physics Requirements and Technical Specifications}

Essential parts of the Jefferson Laboratory (JLab) Hall~B CLAS12~\cite{clas12-nim} physics program, such as
the measurement of parton distribution functions, require tracking of low-momentum  particles with a few percent
momentum resolution and about one degree angle resolution at large angles~\cite{Burkert:2018nvj}. Stable operation
of the tracker at instantaneous luminosities up to 10$^{35}$~cm$^{-2}$s$^{-1}$ is required over a period of roughly
ten years. These requirements are achieved by the central tracker, installed inside the CLAS12 5~T superconducting
solenoid magnet~\cite{magnets-nim}, providing a highly uniform field in the tracking volume and acting as a M{\o}ller
electron shield.

Silicon detector technology provides an excellent match to the central tracking system in the CLAS12 configuration,
where limited space is available and high-luminosity operation is needed for accurate measurements of exclusive
processes at high momentum transfer. The silicon energy band gap (1.12~eV at room temperature) is large enough to
have a low leakage current due to electron-hole pair generation, while it is small enough to allow production of a large
number of charge carriers per unit energy loss of the ionizing particles. The large energy loss per traversed length
of the ionizing particle (3.8~MeV/cm for a minimum-ionizing particle) due to the high material density
(2.33~g/cm$^3$) leads to production of  measurable signals in thin detectors. Because of the high mobility of
electrons and holes, silicon detectors can be used in high-rate environments, with charge collection times on the
order of ns. These characteristics are the main decisive factors leading to large-area applications of silicon sensors
for tracking devices. The expected integrated luminosity per year in CLAS12 is 500~fb$^{-1}$. The radiation dose
for the CLAS12 Silicon Vertex Tracker (SVT) sensors (carbon target) is 2.5~Mrads over a period of 15~years.

The SVT provides tracking capabilities in the CLAS12 Central Detector by measuring recoil baryons, large angle
pions, kaons, and protons, with tracking efficiency $\ge$90\%, transverse momentum resolution
$\delta p_T/p_T \le~5$\%, and angular resolution for polar angles $\delta \theta \le 10--20$~mrad (within
35$^\circ$--125$^\circ$) and azimuthal angles $\delta \phi \le 5$~mrad (within $\ge$90\% of 2$\pi$). The
CLAS12 Central Detector consists of the SVT as the inner detector, surrounded by the Barrel Micromegas Tracker
(BMT)~\cite{mm-nim}, the Central Time-Of-Flight system (CTOF)~\cite{ctof-nim}, and the Central Neutron Detector
(CND)~\cite{cnd-nim}. The required momentum resolution is provided by the SVT, while the BMT improves the polar
angle resolution due to the strips crossing at 90$^\circ$. Note that together the SVT and BMT systems form the
CLAS12 Central Vertex Tracker (CVT). Tracks are matched up with hits in the CTOF system for $\beta$ vs. $p$
measurements (particle identification). The SVT allows for reconstruction of detached vertices, e.g.
$K^0_s \to \pi^+\pi^-$, $\Lambda \to \pi^-p$, $\Xi \to \Lambda\pi$, for an efficient experimental program
in strangeness physics.  

To satisfy the physics requirements on track momentum resolution, the SVT must have low mass inside the acceptance
region. The SVT module position tolerances should be within 20, 500, and 100~$\mu$m across the module, along the
module, and along the beam, respectively.
