\section{Conclusions}

In this paper the GEMC Geant4 implementation of the CLAS12 detector is presented. Thanks to the flexibility of
C++ and Geant4, and the power of object-oriented programming, a detailed Geant4 simulation of the CLAS12 detectors
was developed in which the geometry, digitization, and simulation parameters were decoupled from the code. This
allowed the geometry to be implemented through several sources: native Geant4 volumes, imports from CAD engineering
models, and CLAS12 JAVA geometry services. Realistic detector responses that make use of the data calibration
constants to provide output distributions comparable to the data are included using plugin-like algorithms. The data
acquisition response is reproduced by electronic time window algorithms.

The framework has been shown to perform very well when comparing simulation rates to data and it was an essential
component to optimize the design of the CLAS12 detectors, their associated calibration procedures, and their ultimate
performance. GEMC is an essential tool for improving the significance and accuracy of the physics analyses and for
realizing the science goals of the CLAS Collaboration.

\section{Acknowledgments}

We would like to gratefully acknowledge the Geant4 team for their school workshops and accurate answers to our
questions and problems. This material is based upon work supported by the U.S. Department of Energy, Office of
Science, Office of Nuclear Physics under contract DE-AC05-06OR23177.

